---
title: 'Energy Consumption: Make It Or Break It!'
author: "Corey Dow-Hygelund"
output:
  html_document:
    df_print: paged
---

# Description
**Purpose** To determine if the internal Firefox metrics can be utilized as a proxy for battery drain in the extreme cases. The idea is to investigate if there is a relationship between the metrics and battery drain for cases where   ... (known high and low usage) 

A suite of experiments were performed, which only differed on website
1. Fire up Firefox in Marionette mode
2. Wait 5 minutes
3. Go to website
4. Wait 10 minutes
5. Stop experiment

```{r}
library(jsonlite)
library(lubridate)
library(stringr)

parse_counters_sum <- function(file_path){
  counters <- read_json(file_path)
  df <- data.frame(timestamp=as.POSIXct(character()), seconds=integer(), duration=integer(), counters=integer())
  for (counter in counters){
    duration <- 0
    counts <- 0
    for (tab in counter$tabs) {
      duration = duration + tab$duration
      counts = counts + tab$dispatchCount
    }
    timestamp <- hms(str_split(ymd_hms(counter$timestamp), ' ')[[1]][2])
    seconds <- hour(timestamp)*60*60 + minute(timestamp)*60 + second(timestamp)
    df <- rbind(df, list(timestamp=ymd_hms(counter$timestamp), seconds=seconds, 
                duration=duration, counts=counts))
  }
  return(df)
}

parse_ipg <- function(file_path){
  df <- read.csv(file_path, stringsAsFactors = FALSE)
  clean_time <- hms(str_extract(df$System.Time, '^[0-9]+:[0-9]+:[0-9]+'))
  df$seconds <- (hour(clean_time))*60*60+minute(clean_time)*60+second(clean_time)
  return(df)
}

get_data <- function(counter_file_path, ipg_file_path){
  df.counter <- parse_counters_sum(counter_file_path)
  df.ipg <- parse_ipg(ipg_file_path)

  final <- merge(df.counter, df.ipg, by='seconds')
  final$stopwatch <- final$seconds - final$seconds[1]
  return(final)
}
```


```{r}
root_dir = '/Users/chygelund/PycharmProjects/FF-power-consumption/Energy_Consumption/experiments/intel_pg_battery_report/data/make_or_break/'
```

# Experiment: Low
## www.google.com

```{r echo=FALSE}
counter_file_path <- file.path(root_dir, 'low/run 2/Experiment - V0 - low_6_perf_counters.json')
ipg_file_path <- file.path(root_dir, 'low/run 2/ipg_6_1_clean.txt')
df <- get_data(counter_file_path, ipg_file_path)
```

```{r }
plot(df$stopwatch, df$Cumulative.Processor.Energy_0.mWh.)
plot(df$stopwatch, df$counts)
plot((df$Cumulative.Processor.Energy_0.mWh.), df$counts)
```

 
```{r}
lm(Cumulative.Processor.Energy_0.mWh. ~ stopwatch, df)
```

# Experiment: High
## www.lingscars.com

```{r echo=FALSE}
counter_file_path <- file.path(root_dir, 'high/run 1/Experiment - V0 - high_5_perf_counters.json')
ipg_file_path <- file.path(root_dir, 'high/run 1/ipg_5_1_clean.txt')
df <- get_data(counter_file_path, ipg_file_path)
```

```{r }
plot(df$stopwatch, df$Cumulative.Processor.Energy_0.mWh.)
plot(df$stopwatch, df$counts)
plot((df$Cumulative.Processor.Energy_0.mWh.), df$counts)
```

```{r}
lm(Cumulative.Processor.Energy_0.mWh. ~ stopwatch, df[df$stopwatch<250, ])
```
```{r}
lm(Cumulative.Processor.Energy_0.mWh. ~ stopwatch, df[df$stopwatch>400, ])
```

# Experiment: None
## about:home

```{r echo=FALSE}
counter_file_path <- file.path(root_dir, 'none/run 2/Experiment - V0 - none_7_perf_counters.json')
ipg_file_path <- file.path(root_dir, 'none/run 2/ipg_7_1_clean.txt')
df <- get_data(counter_file_path, ipg_file_path)
```

```{r }
plot(df$stopwatch, df$Cumulative.Processor.Energy_0.mWh.)
plot(df$stopwatch, df$counts)
plot((df$Cumulative.Processor.Energy_0.mWh.), df$counts)
```

```{r}
lm(Cumulative.Processor.Energy_0.mWh. ~ stopwatch, df)
```
