---
title: "Intel Power Gadget to Battery Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xml2)
library(readr)
library(stringr)
library(lubridate)
library(ggplot2)
```

## Description
This simple experiment involved an almost fully charged laptop that was sitting idle. Windows Battery Report was sampled each minute. Intel Power Gadget was started at the beginning, with a duration of one hour. 

### Battery Report
Define functions to extract the most recent `ChargeCapacity` from a Windows Battery Report xml file. 
```{r batt_rep_import}
extract_capacity <- function(xml_file_path){
  xml <- read_file(xml_file_path)
  br <- read_xml(str_remove(xml, 'xmlns=\"http://schemas.microsoft.com/battery/2012\"'))
  ##TODO: Additional filter by attribute EntryType="ReportGenerated" (yields one node)
  entries <- xml_find_all(br, xpath="//RecentUsage/UsageEntry")
  num_entries <- length(entries)
  capacity <- xml_attrs(entries[num_entries])[[1]][c('ChargeCapacity', 'FullChargeCapacity', 'Timestamp')]
  return(capacity)
}

results_dir_path <- 'data/powercomp'
file_paths <- list.files(results_dir_path, '*batter_report_*', full.names=TRUE)

results <- NULL
for (file_path in file_paths){
  iteration = str_match(file_path, 'batter_report_([0-9]+).xml')[,2]
  result <- c(extract_capacity(file_path), as.numeric(iteration))
  names(result) <- c('ChargeCapacity', 'FullChargeCapacity', 'Timestamp', 'Iteration')
  results <- rbind(results, result)
}

results <- data.frame(results[-1, ], stringsAsFactors = FALSE)

results$ChargeCapacity <- as.numeric(results$ChargeCapacity)
results$FullChargeCapacity <- as.numeric(results$FullChargeCapacity)
results$Iteration = as.numeric(results$Iteration)
results$battery_capacity <- results$ChargeCapacity/results$FullChargeCapacity

results <- results[order(results$Iteration),]
```

The data is contained in a sub-directory `data`, and consists of `r length(file_paths)` Battery Report files: a sample for each minute. The xml contains a namespace reference that doesn't exist (oh so Windows!), which needs to be stripped out for xpath queries to work properly.

The timestamps are converted to the number of minutes. This enables easy alignment with the Intel Power Gadget data.

```{r batt_repo_clean}
results$dates <- parse_date_time(results$Timestamp, 'YmdHMS')
results$minutes <- (hour(results$dates)-7)*60+minute(results$dates)
head(results[, c('Iteration', 'minutes', 'ChargeCapacity', 'battery_capacity')], n=10)
```

Updating/resolution of Battery Report appears to be larger than one minute, as can be seen by repeated `battery_capacity` values through time.

### Intel Power Gadget
The data is contained in a single file. It is a standard csv, but there is summary "fluff" at the end that was manually deleted to assist in importing.

```{r ipg_import}
ipg <- read.csv(file.path(results_dir_path, 'powerlog.txt'), stringsAsFactors = FALSE)
ipg$clean_time <- hms(str_extract(ipg$System.Time, '^[0-9]+:[0-9]+:[0-9]+'))
ipg$minutes <- (hour(ipg$clean_time))*60+minute(ipg$clean_time)
```

The Intel Power Gadget data is sampled at a much higher resolution. Therefore, reduce it down to minutes.
```{r ipg_clean}
ipg_comp <- ipg[!duplicated(ipg$minutes), ]
```

Three Intel Power Gadget measurements are processor, IA, and GT energy usage
```{r ipg_plot, echo=FALSE}
ggplot(ipg_comp, aes(minutes, Cumulative.Processor.Energy_0.mWh.)) +
  geom_point()
ggplot(ipg_comp, aes(minutes, Cumulative.IA.Energy_0.mWh.)) +
  geom_point()
ggplot(ipg_comp, aes(minutes, Cumulative.GT.Energy_0.mWh.)) +
  geom_point()
```

## Comparison

Merge the two datasets together.

```{r final}
final <- merge(results, ipg_comp, by='minutes')
```

Compare the battery report `battery_capacity` with the Intel Power Gadget cumulative processor energy

```{r final_plot_1, echo=FALSE}
ggplot(final, aes(battery_capacity, Cumulative.Processor.Energy_0.mWh.)) +
  geom_point()+
  geom_smooth(method='lm')
```

There is a strong relationship between Intel Power Gadget processor energy usage and the Battery Report usage. However, the first 3 Battery Report samples are all constant, despite changes observed in Intel Power Gadget. 

```{r final_plot_2}
final.cost <- final[-(1:3), ]
# plot(final.cost$ratio, final.cost$Cumulative.Processor.Energy_0.mWh., type='l')
ggplot(final.cost, aes(battery_capacity, Cumulative.Processor.Energy_0.mWh.)) +
  geom_point()+
  geom_smooth(method='lm')
```
```{r final_comp}
lm(battery_capacity ~ Cumulative.Processor.Energy_0.mWh., final.cost)
```
## Next Steps
The above trend needs to be observed under differing working conditions, to determine if it holds. 

1. Use Marionette (or other automater) to put demand on the CPU, memory, etc... 
2. Determine the conditions of the observed Battery Report update lag.
