---
title: "Battery Consumption and Firefox Resource API"
output: html_notebook
---

# Description
A suite of experiments were performed under to help determine if the Firefox usage API can be utilized as a proxy for battery consumption. 


Import the libraries used throughout the analysis

```{r, message=FALSE}
library(tibble)
source('../data_munge.R')
library(tidyr)
library(cowplot)
library(magrittr)
```

# Dataset Importing 

Import the experimental data into two separate dataframes: one for performance counters, the other for process information
```{r}
datasets <- get_exp_data(exp_bounds = c(70, 120))
```

# Performance Counters
Let's first examine the peformance counters. 

Aggregate each run for a given URL, then fit a linear model
```{r}
exps <- names(datasets)
perf_agg <- list()
perf_lms <- list()
for (exp in exps){
  runs <- datasets[[exp]]
  df <- datasets[[exp]] %>%
    lapply(function(x) x$perf) %>%
    bind_rows() %>%
    add_column(exp = exp) %>% 
    rename(battery_drain = Cumulative.Processor.Energy_0.mWh.) %>%
    mutate(run_id = as.factor(run_id))
  perf_agg[[exp]] <- df
  perf_lms[[exp]] <- lm(battery_drain ~ counts, df)
}
```

Define a plotter
```{r}
plot_perf_fits <- function(df, exp_name=exp_name){
  p <- ggplot(df, aes(x = counts, y = battery_drain, group=run_id)) +
    geom_smooth(method = "lm", se=TRUE, formula = y ~ x, aes(color=run_id)) +
    geom_point(aes(color=run_id)) +
    labs(title = exp_name)
  return(p)
}
```

```{r}
for (exp_name in exps){
  plot(plot_perf_fits(perf_agg[[exp_name]], exp_name = exp_name) + 
         guides(color=FALSE) +
           xlab('Performance Counts') + 
            ylab('CPU Battery Drain'))
}
```

```{r, fig.width = 8, fig.height = 4}
plot_perf_fits(perf_agg[["exp_gizmodo_article"]], exp_name = 'Gizmodo') + 
         guides(color=FALSE) +
           xlab('Performance Counts') + 
            ylab('CPU Battery Drain')
```

```{r, fig.width = 8, fig.height = 4}
plot_perf_fits(perf_agg[["exp_lingscars"]], exp_name = 'Lingscars') + 
         guides(color=FALSE) +
           xlab('Performance Counts') + 
            ylab('CPU Battery Drain')
```

```{r, fig.width = 8, fig.height = 4}
plot_perf_fits(perf_agg[["exp_rt_article"]], exp_name = 'RT Article') + 
         guides(color=FALSE) +
           xlab('Performance Counts') + 
            ylab('CPU Battery Drain')
```

Plots of Lings, CBC, Slate. 

```{r, fig.width = 8, fig.height = 4}
perf_url_df <- bind_rows(perf_agg[c('exp_cbc_article', 'exp_cbs_article', 'exp_lingscars', 'exp_slate')])
ggplot(perf_url_df[perf_url_df$run_id < 5, ], aes(x = counts, y = battery_drain)) +
    geom_point(aes(shape=run_id, color=exp)) +
    guides(shape=FALSE)+
           xlab('Performance Counts') + 
            ylab('CPU Battery Drain')

```


```{r}
perf_url_df <- bind_rows(perf_agg[c('exp_cbc_article', 'exp_cbs_article', 'exp_lingscars', 'exp_slate', 
                                    'exp_livescience_article', 'exp_gizmodo_article', 'exp_cnet_article')])
ggplot(perf_url_df[perf_url_df$run_id < 5, ], aes(x = counts, y = battery_drain)) +
    geom_point(aes(shape=run_id, color=exp)) 

```

# Process Information

## Child threads
Investigate the difference in slopes between the runs of `exp_rt`, under the light of the process information.

As per Tarek, child threads are the likely culprit.

Isolate `exp_rt_article` and examine the child thread counts through time.

```{r, fig.width = 12, fig.height = 8}
rt_exp = datasets[['exp_rt_article']]

get_num_child_threads <- function(measure){
  threads = NULL
  for(child in measure$processes$process$children){
    threads <- c(threads, length(child$threads))
  }
  return(threads)
}

runs <- 1:length(rt_exp)
plots <- list()
for(run in runs){
  # build the plotting df
  seconds <- get_seconds(rt_exp[[run]]$process)
  num_ct.df <- sapply(rt_exp[[run]]$process, get_num_child_threads)  %>%
    data.frame %>% 
    t %>% 
    as.data.frame %>%
    set_colnames(str_replace(names(.), 'V', 'Child_')) %>%
    mutate(seconds = seconds) %>%
    gather('child', 'num_threads', -seconds )
  # plot it
  p <- ggplot(num_ct.df, aes(x=seconds, y=num_threads, group=child)) +
    geom_line() + 
    geom_point(aes(color=child)) + 
    theme_bw() +
    labs(title=paste('Run', run)) + 
    ylab('# of Threads') + 
    ylim(10, 50) + 
    geom_vline(xintercept=60, linetype='dashed', color='black')
  if (run == 1) p <- p + theme(legend.position = c(0.18, 0.75))
  else p <- p + guides(color=FALSE)
    
  plots[[run]] <- p 
}

print(plot_grid(plotlist = (plots)))
```


**Observation**: 
* Child 3 (blue, content) is where the action lies at navigation to URL
* Runs 1 and 4 have slightly _more_ threads than 2 and 3.
  - 1 and 4 have smaller counter dependency on battery usage
* Child 2 and 3 do differ at 60s, however they trend differently (run 1 lowest, 2 and 4 same, 3 highest)

Next, let's examine these differences in the content threads observed.

Define the custom data munge functions for content thead
```{r}

build_child_threads_df <- function(measures){
  # Builds a dataframe of the child threads throughout the experiment
  # Args:
  #   measures: list of experimental run results. returned from jsonlite::read_json(<exp file>)
  # Returns: 
  #   data.frame of child threads. columns: type (cpuKernel or cpuUser), measure (reported value), second, tid, name
  seconds <- get_seconds(measures)
  df <- NULL
  for(i in 1:length(measures)){
    measure = measures[[i]]
    df <- rbind(df, t(sapply(measure$processes$process$children[[3]]$thread, function(x) c(unlist(x), second=seconds[i]))))
  }
  
  df <- df %>%
    data.frame(stringsAsFactors = FALSE) %>%
    mutate_at(.vars = vars(cpuKernel, cpuUser, second), .funs= funs(as.numeric)) %>%
    arrange(second) %>%
    gather("type", "measure", -tid, -second, -name)
  return(df)
}

get_memory_sizes <- function(measure){
  x <- measure$processes$process
  return(c(virtual=x$virtualMemorySize, resident=x$residentSetSize))
}

# Define functions to calculate the difference in this cumulative value across time.
calc_diff <- function(x){
  delta <- diff(x$measure)
  time <- x$second[2:nrow(x)]
  name <- unique(x$name)[1]
  if (length(time) != length(delta)) 
    df <- data.frame(delta=as.numeric(), second=as.numeric(), name=character(), stringsAsFactors = FALSE)
  else 
    df <- data.frame(delta=delta, second=time, name = name, stringsAsFactors = FALSE)
  return(df)
  }

calc_thread_diff <- function(df){
  # Calculates the difference between each sample of a child thread 
  # Args:
  #   measures: data.frame returned by `build_chlid_threads_df`
  # Returns: 
  #   data.frame of child threads. columns: type (cpuKernel or cpuUser), measure (reported value), second, tid, name
  df %>%
    group_by(tid, type) %>%
    do(calc_diff(.)) -> c.diff
  return(c.diff)
}
```

Apply them across experiments
```{r}
child_threads <- list()
child_measures <- list()
for(exp in names(datasets)){
  child_threads[[exp]] <- lapply(datasets[[exp]], function(x) build_child_threads_df(x$process))
  child_measures[[exp]] <- lapply(child_threads[[exp]], calc_thread_diff)
}
```

Build a general purpose plotting function
```{r}
plot_child_threads <- function(child_threads_df, ymax, p_names, xlimits, metric = 'measure', type='cpuKernel'){
  plots <- list()
  for(run in 1:length(child_threads_df)){
    exp <- child_threads_df[[run]]
    if (!missing(p_names)) exp <- exp[exp$name %in% p_names, ]
    p <- ggplot(exp[exp$type==type & exp[metric]>0, ], aes(x=second, y=get(metric)))+
      # geom_line() +
      geom_point(aes(color=name))+
      theme_bw()+
      labs(title=paste(type, ': Run', run)) +
      ylab(metric) 
    if (!missing(ymax)) p <- p + ylim(0, ymax)
    if (!missing(xlimits)) p <- p + xlim(xlimits[1], xlimits[2])
    plots[[run]] <- p
  }
  print(plot_grid(plotlist = plots))
}
```

Take a look at `exp_rt`
```{r}
rt_child_threads <- child_threads[['exp_rt_article']]
rt_measure <- child_measures[['exp_rt_article']]
head(rt_child_threads[[1]])

```

```{r}
lapply(rt_child_threads, function(x) table(x[x$second==74, ]$name ))
```


As per Tarek, many of threads are unnamed. We can see that there are two more unnamed threads for runs 1 and 4, that aren't in 2 and 3. There is also Cameras IPC threads in 1 and 4, missing in 2 and 3.  (Look at aggregated counts on these threads). 

## CPU Time
The measure column is the "time spent in nanoseconds by this thread in CPU time". Hence it is a measure of demand. Let's examine this one, focusing initially on the threads above. Let's examine this measure for threads when non-zero.

### Child Threads: Maximum measure
Find what are dominating the measures for each experiment:
```{r}
get_dominate_thread <- function(df, metric='measure', ctype='cpuUser'){
  d <- df %>%
    filter(type==ctype) %>%
    arrange(desc(get(metric))) %>%
    group_by(name) %>%
    slice(1) %>%
    arrange(desc(get(metric)))
  return(head(d, n=5))
}

```
#### Delta, cpuUser
```{r}
cpuUser_delta_top <- list()
for(exp_name in names(child_measures)){
  exp <- child_measures[[exp_name]]
  cpuUser_delta_top[[exp_name]] <- exp %>%
    lapply(get_dominate_thread, metric='delta', ctype='cpuUser') %>%
    bind_rows()
}

cpuKernel_delta_top <- list()
for(exp_name in names(child_measures)){
  exp <- child_measures[[exp_name]]
  cpuKernel_delta_top[[exp_name]] <- exp %>%
    lapply(get_dominate_thread, metric='delta', ctype='cpuKernel') %>%
    bind_rows()
}

```

```{r}
cpuKernel_delta_top[['exp_rt_article']]%>% arrange(delta) %>% distinct(name)
```

```{r}
cpuUser_delta_top[['exp_rt_article']]%>% arrange(delta) %>% distinct(name)
```

```{r}
plot_perf_fits(perf_agg[["exp_rt_article"]], exp_name = 'RT Article') + 
  labs(title='RT Article') +
  xlab('Performance Counts') + 
  ylab('CPU Battery Drain')
```


```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(rt_child_threads, ymax = 2.5e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(rt_child_threads, p_names = p_names)
```

This pattern matches the observed counters:
* Unnamed thread significant higher for runs 1 and 4
* Run 4 has much higher than both unnamed and Chrome_ChildThread

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(rt_measure, p_names = p_names, metric = 'delta', ymax=1.25e8)
```

**Hypothesis**:
*`Chrome_ChildThread` dominates battery usage. 
* The `JS Helper` and `Socket Thread` are pushing the battery usage to higher usage values for 1 and 4.
* The unnamed thread is creating a bunch of counts that _don't_ contribute to battery usage.
  - Higher slope => lower battery slope

Look at the User threads

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'Socket Thread', 'JS Helper', 'PaintThread', 'ImgDecoder #1')
plot_child_threads(rt_child_threads, ymax=5e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('Chrome_ChildThread', 'Socket Thread', 'JS Helper', 'PaintThread') #, 'ImgDecoder #1')
plot_child_threads(rt_child_threads, 1e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'Socket Thread', 'JS Helper', 'PaintThread', 'ImgDecoder #1')
plot_child_threads(rt_measure, p_names = p_names, metric = 'delta', type='cpuUser', ymax=1.1e9)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'Socket Thread', 'JS Helper')
plot_child_threads(rt_measure, metric = 'delta', type='cpuUser', ymax=1.1e9, xlimits=c(70, 120),  p_names = p_names)
```

Bizarre behavior with unnamed thread, but is consistent with 1/4, 2/3 groups. Again, `JS_Helper` is much higher for 4, and less so for 1, then 2 and 3. `Chrome_ChildThread` consistent in this case. 

## `livescience_article`
Test hypothesis on another URL with similar behavior: `exp_livescience_article`
```{r}
cpuKernel_delta_top[['exp_livescience_article']]%>% arrange(delta) %>% distinct(name)
```

```{r}
cpuUser_delta_top[['exp_livescience_article']]%>% arrange(delta) %>% distinct(name)
```

```{r}
plot_perf_fits(perf_agg[["exp_livescience_article"]], exp_name = 'Livescience Article') + 
  labs(title='Livescience Article') +
  xlab('Performance Counts') + 
  ylab('CPU Battery Drain')
```

```{r, fig.width = 12, fig.height = 8}
livescience_child_threads <- child_threads[['exp_livescience_article']]
livescience_measure <- child_measures[['exp_livescience_article']]
  
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(livescience_child_threads, ymax = 2.5e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(livescience_measure, ymax=2e8, p_names = p_names, metric = 'delta')
```


SWEET! Consistent with theory:
* Higher `Chrome_ChildThread` on 1 leads to higher net usage. 
* Hihger unnamed thread leads to higher counter usage. 

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(livescience_child_threads, ymax = 4.5e9, p_names = p_names, type='cpuUser')
```


```{r, fig.width = 12, fig.height = 8}
p_names <- c('Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(livescience_child_threads, ymax = 1e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(livescience_measure, p_names = p_names, metric = 'delta', type='cpuUser')
```

**Observation**
* Eratic behavior in no name thread aligns with lower slope

## `exp_espncricinfo`
```{r}
cpuKernel_delta_top[["exp_espncricinfo"]]%>% arrange(delta) %>% distinct(name)
```

```{r}
cpuUser_delta_top[['exp_espncricinfo']]%>% arrange(delta) %>% distinct(name)
```

```{r}
plot_perf_fits(perf_agg[['exp_espncricinfo']], exp_name = 'exp_espncricinfo')+  
  labs(title='ESPN CriInfo') +
  xlab('Performance Counts') + 
  ylab('CPU Battery Drain')
```


```{r, fig.width = 12, fig.height = 8}
espncri_child_thread = child_threads[['exp_espncricinfo']]

p_names <- c('', 'Chrome_ChildThread', 'Socket Thread', 'PaintThread')
plot_child_threads(espncri_child_thread, ymax=2.5e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('Chrome_ChildThread', 'Socket Thread', 'PaintThread')
plot_child_threads(espncri_child_thread, 1.5e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c("", "Chrome_ChildThread", 'SocketThread', "ImgDecoder #2", "StyleThread#0", "StyleThread#1", "StyleThread#2", "PaintThread", "JS Helper")
plot_child_threads(espncri_child_thread, ymax = 5e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c("Chrome_ChildThread", 'SocketThread', "ImgDecoder #2", "StyleThread#0", "StyleThread#1", "StyleThread#2", "PaintThread", "JS Helper")

plot_child_threads(espncri_child_thread, ymax=1.5e9, p_names = p_names, type='cpuUser')
```


## `nytimes`
```{r}
cpuKernel_delta_top[['exp_nytimes']]%>% arrange(delta) %>% distinct(name)
```

```{r}
cpuUser_delta_top[['exp_nytimes']]%>% arrange(delta) %>% distinct(name)
```

```{r}
plot_perf_fits(perf_agg[['exp_nytimes']], exp_name = 'exp_nytimes')+
    labs(title='NY Times') +
  xlab('Performance Counts') + 
  ylab('CPU Battery Drain')
```


```{r, fig.width = 12, fig.height = 8}
nyt_child_threads = child_threads[['exp_nytimes']]

p_names <- c('', 'Chrome_ChildThread', 'Socket Thread', 'JS Helper', 'DOM Worker', 'MediaPlayback #2', 'PaintThread')
plot_child_threads(nyt_child_threads, ymax = 1.75e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('Socket Thread', 'JS Helper', 'DOM Worker', 'PaintThread') #, 'MediaPlayback #2')
plot_child_threads(nyt_child_threads, ymax = 3e8, p_names = p_names)
```

 **Observation**
* No name thread again associated with increased counters: 4 is least, however 1 and 3 _don't_ add up.  
* `Chrome_ChildThread` associated with highest usage (2), but not by much. 
* Also, not counters much less than previous two site
* Something funny with this one!

```{r, fig.width = 12, fig.height = 8}
p_names <- c("", "Chrome_ChildThread", "MediaPlayback #1", "ImgDecoder #2", "StyleThread#0","PaintThread", "DOM Worker", "ImgDecoder #1","JS Helper")
plot_child_threads(nyt_child_threads, ymax = 5e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c("Chrome_ChildThread", "ImgDecoder #2", "StyleThread#0","PaintThread", "DOM Worker", "ImgDecoder #1","JS Helper") #"MediaPlayback #1", 
plot_child_threads(nyt_child_threads, ymax = 1e9, p_names = p_names, type='cpuUser')
```

* Erratic no-name thread associated with lowest slope 

## `cbc_article`
```{r, fig.width = 12, fig.height = 8}
cbc_child_threads <- child_threads[['exp_cbc_article']]


p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(cbc_child_threads, ymax = 3e9, p_names = p_names)
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(cbc_child_threads, ymax = 5e9, p_names = p_names, type='cpuUser')
```

## `lingscars`
```{r, fig.width = 12, fig.height = 8}
lingscars_exp = datasets[['exp_lingscars']]
lingscars_child_threads <- lapply(lingscars_exp, function(x) build_child_threads_df(x$process))
lingscars_measure <- lapply(lingscars_child_threads, calc_thread_diff)

p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(lingscars_child_threads, ymax = 1.5e9, p_names = p_names)
```

```{r}
exp <- lingscars_child_threads[[1]]
p <- ggplot(exp[exp$type=='cpuKernel' & exp['measure']>0, ], aes(x=second, y=measure))+
      # geom_line() +
      geom_point(aes(color=name))+
      theme_bw()
print(p)
```


```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(lingscars_measure, ymax=1.5e8, p_names = p_names, metric = 'delta')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper', 'PaintThread')
plot_child_threads(lingscars_measure, p_names = p_names, metric = 'delta')
```

**Observation**
* Lingscars has _lower_ measure values! 
* However, socket thread is heavily used
* All no-name threads have same slope

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(lingscars_child_threads, ymax = 5e9, p_names = p_names, type='cpuUser')
```

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread','Socket Thread', 'JS Helper', 'PaintThread', 'StyleThread#2', 'StyleThread#1')
plot_child_threads(lingscars_measure, ymax=1.5e9, p_names = p_names, metric = 'delta', type='cpuUser')
```

## `google`
```{r}
cpuKernel_delta_top[['exp_google']]%>% arrange(delta) %>% distinct(name)
```

```{r}
plot_perf_fits(perf_agg[['exp_google']], exp_name = 'exp_nytimes')
```


```{r, fig.width = 12, fig.height = 8}
google_child_threads = child_threads[['exp_google']]

p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'JS Helper', 'Socket Thread', 'Paint Thread')
plot_child_threads(google_child_threads, ymax = 8e8, p_names = p_names)
```

 **Observation**
* No name thread again associated with increased counters: 4 is least, however 1 and 3 _don't_ add up.  
* `Chrome_ChildThread` associated with highest usage (2), but not by much. 
* Also, not counters much less than previous two site
* Something funny with this one!

```{r, fig.width = 12, fig.height = 8}
p_names <- c('', 'Chrome_ChildThread', 'StreamTrans #2', 'Socket Thread', 'JS Helper')
plot_child_threads(nyt_child_threads, ymax = 5e9, p_names = p_names, type='cpuUser')
```


# Modeling 

First look into a simple model: relate to overall battery drain
* Look at net deltas for named threads across experiment
* Ignore unnamed threads
* Ignore performance counters while ignore performance counters)

Calculate overall battery drain

```{r}

total_battery_drain <- list()
for(exp_name in names(perf_agg)){
  battery_delta <- perf_agg[[exp_name]] %>%
    group_by(run_id) %>%
    summarize(drain = diff(range(battery_drain))[1]) %>%
    mutate(run_id = as.numeric(run_id)) %>%
    add_column(exp=exp_name)
  total_battery_drain[[exp_name]] <- battery_delta
t_b_df <- bind_rows(total_battery_drain)
}
```

```{r, results='axis'}
knitr::kable(t_b_df %>%
  group_by(exp) %>%
  summarize(drain = mean(drain)) %>%
  arrange(desc(drain)))
```

Next, build the aggregate child thread features

```{r}

child_measures_features<-function(exp_name, dfs){
  exps <- list()
  exp <- dfs[[exp_name]]
  for(run_id in 1:length(exp)){
    exp[[run_id]] %>%
      mutate(delta=replace(delta, delta<0, 0)) %>%
      filter(name != '' & second > 70 & second < 120) %>%
      group_by(type) %>%
      summarise(sum = sum(delta)) %>%
      add_column(run_id = run_id, exp = exp_name) -> result
    exps[[run_id]] <- result
  }
  return(bind_rows(exps))
}
c_features <- lapply(names(child_measures), child_measures_features, dfs = child_measures)
```

```{r}
c_features_df <- bind_rows(c_features) %>% 
  arrange(desc(sum))
c_features_df
```

```{r, fig.width = 8, fig.height = 4}
features_m1 <- c_features_df %>%
  inner_join(t_b_df)

f_m1_cpuUser <- features_m1[features_m1$type=='cpuUser', ]
ggplot(f_m1_cpuUser, aes(sum, drain))+
  geom_point(aes(color=exp)) + 
  geom_smooth(method = "lm", se=TRUE, formula = y ~ x)+
  ylab('CPU Total Battery Drain') + 
  xlab('named child thread sum')+
  labs(title='cpuUser') +
  guides(color=FALSE)
```

```{r, fig.width = 8, fig.height = 4}
ggplot(f_m1_cpuUser[f_m1_cpuUser$sum < 1.5e10, ], aes(sum, drain))+
  geom_point(aes(color=exp)) + 
  geom_smooth(method = "lm", se=TRUE, formula = y ~ x)+
  ylab('CPU Total Battery Drain') + 
  xlab('named child thread sum')+
  labs(title='cpuUser') +
  guides(color=FALSE)
```

```{r, fig.width = 8, fig.height = 4}
f_m1_cpuKernel <- features_m1[features_m1$type=='cpuKernel', ]
ggplot(f_m1_cpuKernel, aes(sum, drain))+
  geom_point(aes(color=exp)) + 
  geom_smooth(method = "lm", se=TRUE, formula = y ~ x)+
  guides(color=FALSE) +
  labs(title = 'cpuKernel') + 
  ylab('CPU Total Battery Drain') + 
  xlab('named child thread sum')
  
```


```{r, fig.width = 8, fig.height = 4}
ggplot(f_m1_cpuKernel[f_m1_cpuKernel$sum <4e9, ], aes(sum, drain))+
  geom_point(aes(color=exp)) + 
  geom_smooth(method = "lm", se=TRUE, formula = y ~ x)+
  guides(color=FALSE) +
  labs(title = 'cpuKernel') + 
  ylab('CPU Total Battery Drain') + 
  xlab('named child thread sum')
  
```

```{r, fig.width = 7, fig.height = 4}
features_m1 %>%
  spread(type, sum) -> features_m1_spread

full_lm <- lm(drain ~ cpuKernel + cpuUser, features_m1_spread)
features_m1_spread$predictions <- predict(full_lm)
ggplot(features_m1_spread, aes(predictions, drain)) +
  geom_point(aes(color=exp))+
  guides(color=FALSE) + 
  geom_abline(slope=1, linetype='dashed', color='black') +
  xlab('Model Prediction') + 
  ylab('CPU Total Battery Drain') 

```

**Next**
_Add in performance counters (mean difference or sum of steady state)_


Upon looking at the child thread behavior, an initial predictive model can be proposed. 

## Feature generation
The feature set is as follows:
* Performance Counters
* Difference of Chrome_childThread: cpuKernel
* Difference of Chrome_childThread: cpuUser (deal with resetting)
* Difference of sum of no-name thread
* Difference of sum of JS Helper threads.
* Difference of sum of socket threads
* Difference of other threads: cpuUser and cpuKernel

# ```{r}
# generate_m1_features <- (c_df, delta_df, perf_df){
#   
# }
# ```



**TODO**
1. Fit lines to chrome thread: see if that can predict net end use (i.e., delta battery/delta time)
2. Fit linear model (random forest): counter, diff of child thread, JS helper, socket, no name
   - features:
    - Difference of Chrome_childThread: cpuKernel
    - Difference of Chrome_childThread: cpuUser (deal with resetting)
    - Difference of sum of no-name thread
    - Difference of sum of JS Helper threads.
    - Difference of sum of socket threads
    - Difference of other threads: cpuUser and cpuKernel
   - Slope of resets in cpuUser appears to be associated with higher usage!
     - In all cases, other than lingscars and cbc, associated with lesser slope


** Next steps **
* Look at additional thread names for features
* Additional feature: previous positive socket/js thread values


**TODO**
1. Create the distribution of lm coefficients for high R2
   - Note that NYT has odd behaviour, youtube, bbc, (variation from low to high)
   - Some of the fits have wonky behavior: popsci, 
2. Examine # of parent processes, memory, etc...
3. Examine child processes for similar URL with crazy change in slope!
4. Give why Lingscars, Twitch so heavy


